Predicting how climate change will affect how and where terrestrial mammals will move in British Columbia, Canada

### 2025-05-07 writing/manuscript.Rmd
fixed tucker ref

Together, the predicted changes in distance traveled and habitat selection indicate that climate change will have complex consequences for populations as well as cascade effects within ecosystems as species adapt to the changing environments [or fail to do so: @botero_evolutionary_2015; @polazzo_measuring_2024]. The resulting changes in mammalian movement behaviour will have ramifications in individuals' encounter rates [@hou_cold_2020; @martinez-garcia_how_2020], population dynamics [@needs_ref], and food webs [@needs_ref] as landscapes change and animals face increasing pressures from human activity [@sih_evolution_2011], including habitat fragmentation [@needs_ref], habitat loss [@needs_ref], and greater human presence in wild spaces [@weststrate_how_2024; @rosenthal_impact_2022; @rice_conspicuous_2022].

***Cite @tucker_moving_2018***

>>>>

Together, the predicted changes in distance traveled and habitat selection indicate that climate change will have complex consequences for populations as well as cascade effects within ecosystems as species adapt to the changing environments [or fail to do so: @botero_evolutionary_2015; @polazzo_measuring_2024]. The resulting changes in mammalian movement behaviour will have ramifications in individuals' encounter rates [e.g., @hou_cold_2020; @martinez-garcia_how_2020], population dynamics [@needs_ref], and food webs [@needs_ref] as landscapes change and animals face increasing pressures from human activity [@sih_evolution_2011; @tucker_moving_2018], including habitat fragmentation [@needs_ref], habitat loss [@needs_ref], and greater human presence in wild spaces [@weststrate_how_2024; @rosenthal_impact_2022; @rice_conspicuous_2022].
